Algorithm Selection for Graph Algorithms

### 2015-12-09 portfolio/as-graphs.Rnw
include more information

<<echo=FALSE, results='asis', warning=FALSE, message=FALSE>>=
resvbs = data.frame(model = "virtual best",
    mean.performance = mean(parscores(ldf, vbs, factor = 1)),
    median.performance = median(parscores(ldf, vbs, factor = 1)))
ressb = data.frame(model = "single best",
    mean.performance = mean(parscores(ldf, singleBest, factor = 1)),
    median.performance = median(parscores(ldf, singleBest, factor = 1)))

@@

modelc = classify(rflearner, ldf)
resc = data.frame(model = "classification",
    mean.performance = mean(parscores(ldf, modelc, factor = 1)),
    median.performance = median(parscores(ldf, modelc, factor = 1)))
times = sapply(modelc$models, function(x) row.names(sortByCol(as.data.frame(x$learner.model$importance), "MeanDecreaseGini", asc = FALSE))[1])
print(xtable(as.table(sort(table(times), decreasing = TRUE)), caption = "Most important features for classification."), booktabs = TRUE)

modelr = regression(makeLearner("regr.randomForest"), ldf)
resr = data.frame(model = "regression",
    mean.performance = mean(parscores(ldf, modelr, factor = 1)),
    median.performance = median(parscores(ldf, modelr, factor = 1)))
times = sapply(modelr$models, function(x) row.names(sortByCol(as.data.frame(x$learner.model$importance), "IncNodePurity", asc = FALSE))[1])
print(xtable(as.table(sort(table(times), decreasing = TRUE)), caption = "Most important features for regression."), booktabs = TRUE)

modelcp = classifyPairs(rflearner, ldf)
rescp = data.frame(model = "classifyPairs",
    mean.performance = mean(parscores(ldf, modelcp, factor = 1)),
    median.performance = median(parscores(ldf, modelcp, factor = 1)))
times = sapply(modelcp$models, function(x) row.names(sortByCol(as.data.frame(x$learner.model$importance), "MeanDecreaseGini", asc = FALSE))[1])
print(xtable(as.table(sort(table(times), decreasing = TRUE)), caption = "Most important features for classificationPairs."), booktabs = TRUE)

modelrp = regressionPairs(makeLearner("regr.randomForest"), ldf)
resrp = data.frame(model = "regressionPairs",
    mean.performance = mean(parscores(ldf, modelrp, factor = 1)),
    median.performance = median(parscores(ldf, modelrp, factor = 1)))
times = sapply(modelrp$models, function(x) row.names(sortByCol(as.data.frame(x$learner.model$importance), "IncNodePurity", asc = FALSE))[1])
print(xtable(as.table(sort(table(times), decreasing = TRUE)), caption = "Most important features for regressionPairs."), booktabs = TRUE)

@@

pmod = mod$predictions
pmod$portfolio = parscores(ldf, mod, factor = 1)
pmod$iteration = NULL
pmod$algorithm = NULL
pmod$score = NULL

perfs = subset(ldf$data, TRUE, c("instance_id", ldf$performance))
perfs = merge(perfs, vbs.agg, by = "instance_id")
perfs = merge(perfs, pmod, by = "instance_id")
wide = gather_(perfs, "solver", "time", names(perfs)[-1])
ggplot(wide, aes(x = time, col = solver)) + stat_ecdf() + scale_x_log10() +
    ylab("fraction of instances solved")
@

@@

<<echo=FALSE, results='asis', warning=FALSE, message=FALSE>>=
resvbs = data.frame(model = "virtual best",
    mean.performance = mean(parscores(ldf3, vbs, factor = 1)),
    median.performance = median(parscores(ldf3, vbs, factor = 1)))
ressb = data.frame(model = "single best",
    mean.performance = mean(parscores(ldf3, singleBest, factor = 1)),
    median.performance = median(parscores(ldf3, singleBest, factor = 1)))

modelc = classify(rflearner, ldf3)
resc = data.frame(model = "classification",
    mean.performance = mean(parscores(ldf3, modelc, factor = 1)),
    median.performance = median(parscores(ldf3, modelc, factor = 1)))
times = sapply(modelc$models, function(x) row.names(sortByCol(as.data.frame(x$learner.model$importance), "MeanDecreaseGini", asc = FALSE))[1])
print(xtable(as.table(sort(table(times), decreasing = TRUE)), caption = "Most important features for classification."), booktabs = TRUE)

modelr = regression(makeLearner("regr.randomForest"), ldf3)
resr = data.frame(model = "regression",
    mean.performance = mean(parscores(ldf3, modelr, factor = 1)),
    median.performance = median(parscores(ldf3, modelr, factor = 1)))
times = sapply(modelr$models, function(x) row.names(sortByCol(as.data.frame(x$learner.model$importance), "IncNodePurity", asc = FALSE))[1])
print(xtable(as.table(sort(table(times), decreasing = TRUE)), caption = "Most important features for regression."), booktabs = TRUE)

modelcp = classifyPairs(rflearner, ldf3)
rescp = data.frame(model = "classifyPairs",
    mean.performance = mean(parscores(ldf3, modelcp, factor = 1)),
    median.performance = median(parscores(ldf3, modelcp, factor = 1)))
times = sapply(modelcp$models, function(x) row.names(sortByCol(as.data.frame(x$learner.model$importance), "MeanDecreaseGini", asc = FALSE))[1])
print(xtable(as.table(sort(table(times), decreasing = TRUE)), caption = "Most important features for classificationPairs."), booktabs = TRUE)

modelrp = regressionPairs(makeLearner("regr.randomForest"), ldf3)
resrp = data.frame(model = "regressionPairs",
    mean.performance = mean(parscores(ldf3, modelrp, factor = 1)),
    median.performance = median(parscores(ldf3, modelrp, factor = 1)))
times = sapply(modelrp$models, function(x) row.names(sortByCol(as.data.frame(x$learner.model$importance), "IncNodePurity", asc = FALSE))[1])
print(xtable(as.table(sort(table(times), decreasing = TRUE)), caption = "Most important features for regressionPairs."), booktabs = TRUE)

@@

@@

pmod = mod$predictions
pmod$portfolio = parscores(ldf3, mod, factor = 1)
pmod$iteration = NULL
pmod$algorithm = NULL
pmod$score = NULL

perfs = subset(ldf3$data, TRUE, c("instance_id", ldf3$performance))
perfs = merge(perfs, vbs.agg, by = "instance_id")
perfs = merge(perfs, pmod, by = "instance_id")
wide = gather_(perfs, "solver", "time", names(perfs)[-1])
ggplot(wide, aes(x = time, col = solver)) + stat_ecdf() + scale_x_log10() +
    ylab("fraction of instances solved")
@

@@

<<echo=FALSE, results='asis', warning=FALSE, message=FALSE>>=
resvbs = data.frame(model = "virtual best",
    mean.performance = mean(parscores(ldf2, vbs, factor = 1)),
    median.performance = median(parscores(ldf2, vbs, factor = 1)))
ressb = data.frame(model = "single best",
    mean.performance = mean(parscores(ldf2, singleBest, factor = 1)),
    median.performance = median(parscores(ldf2, singleBest, factor = 1)))

modelc = classify(rflearner, ldf2)
resc = data.frame(model = "classification",
    mean.performance = mean(parscores(ldf2, modelc, factor = 1)),
    median.performance = median(parscores(ldf2, modelc, factor = 1)))
times = sapply(modelc$models, function(x) row.names(sortByCol(as.data.frame(x$learner.model$importance), "MeanDecreaseGini", asc = FALSE))[1])
print(xtable(as.table(sort(table(times), decreasing = TRUE)), caption = "Most important features for classification."), booktabs = TRUE)

modelr = regression(makeLearner("regr.randomForest"), ldf2)
resr = data.frame(model = "regression",
    mean.performance = mean(parscores(ldf2, modelr, factor = 1)),
    median.performance = median(parscores(ldf2, modelr, factor = 1)))
times = sapply(modelr$models, function(x) row.names(sortByCol(as.data.frame(x$learner.model$importance), "IncNodePurity", asc = FALSE))[1])
print(xtable(as.table(sort(table(times), decreasing = TRUE)), caption = "Most important features for regression."), booktabs = TRUE)

modelcp = classifyPairs(rflearner, ldf2)
rescp = data.frame(model = "classifyPairs",
    mean.performance = mean(parscores(ldf2, modelcp, factor = 1)),
    median.performance = median(parscores(ldf2, modelcp, factor = 1)))
times = sapply(modelcp$models, function(x) row.names(sortByCol(as.data.frame(x$learner.model$importance), "MeanDecreaseGini", asc = FALSE))[1])
print(xtable(as.table(sort(table(times), decreasing = TRUE)), caption = "Most important features for classificationPairs."), booktabs = TRUE)

modelrp = regressionPairs(makeLearner("regr.randomForest"), ldf2)
resrp = data.frame(model = "regressionPairs",
    mean.performance = mean(parscores(ldf2, modelrp, factor = 1)),
    median.performance = median(parscores(ldf2, modelrp, factor = 1)))
times = sapply(modelrp$models, function(x) row.names(sortByCol(as.data.frame(x$learner.model$importance), "IncNodePurity", asc = FALSE))[1])
print(xtable(as.table(sort(table(times), decreasing = TRUE)), caption = "Most important features for regressionPairs."), booktabs = TRUE)

@@

@@

pmod = mod$predictions
pmod$portfolio = parscores(ldf2, mod, factor = 1)
pmod$iteration = NULL
pmod$algorithm = NULL
pmod$score = NULL

perfs = subset(ldf2$data, TRUE, c("instance_id", ldf2$performance))
perfs = merge(perfs, vbs.agg, by = "instance_id")
perfs = merge(perfs, pmod, by = "instance_id")
wide = gather_(perfs, "solver", "time", names(perfs)[-1])
ggplot(wide, aes(x = time, col = solver)) + stat_ecdf() + scale_x_log10() +
    ylab("fraction of instances solved")
@

>>>>

<<echo=FALSE, results='asis', warning=FALSE, message=FALSE>>=
resvbs = data.frame(model = "virtual best",
    mean.misclassification.penalty = mean(misclassificationPenalties(ldf, vbs)),
    solved = sum(successes(ldf, vbs)),
    mean.performance = mean(parscores(ldf, vbs, factor = 1)),
    median.performance = median(parscores(ldf, vbs, factor = 1)))
ressb = data.frame(model = "single best",
    mean.misclassification.penalty = mean(misclassificationPenalties(ldf, singleBest)),
    solved = sum(successes(ldf, singleBest)),
    mean.performance = mean(parscores(ldf, singleBest, factor = 1)),
    median.performance = median(parscores(ldf, singleBest, factor = 1)))

@@

modelc = classify(rflearner, ldf)
resc = data.frame(model = "classification",
    mean.misclassification.penalty = mean(misclassificationPenalties(ldf, modelc)),
    solved = sum(successes(ldf, modelc)),
    mean.performance = mean(parscores(ldf, modelc, factor = 1)),
    median.performance = median(parscores(ldf, modelc, factor = 1)))
times = sapply(modelc$models, function(x) row.names(sortByCol(as.data.frame(x$learner.model$importance), "MeanDecreaseGini", asc = FALSE))[1])
print(xtable(as.table(sort(table(times), decreasing = TRUE)), caption = "Most important features for classification."), booktabs = TRUE)

modelr = regression(makeLearner("regr.randomForest"), ldf)
resr = data.frame(model = "regression",
    mean.misclassification.penalty = mean(misclassificationPenalties(ldf, modelr)),
    solved = sum(successes(ldf, modelr)),
    mean.performance = mean(parscores(ldf, modelr, factor = 1)),
    median.performance = median(parscores(ldf, modelr, factor = 1)))
times = sapply(modelr$models, function(x) row.names(sortByCol(as.data.frame(x$learner.model$importance), "IncNodePurity", asc = FALSE))[1])
print(xtable(as.table(sort(table(times), decreasing = TRUE)), caption = "Most important features for regression."), booktabs = TRUE)

modelcp = classifyPairs(rflearner, ldf)
rescp = data.frame(model = "classifyPairs",
    mean.misclassification.penalty = mean(misclassificationPenalties(ldf, modelcp)),
    solved = sum(successes(ldf, modelcp)),
    mean.performance = mean(parscores(ldf, modelcp, factor = 1)),
    median.performance = median(parscores(ldf, modelcp, factor = 1)))
times = sapply(modelcp$models, function(x) row.names(sortByCol(as.data.frame(x$learner.model$importance), "MeanDecreaseGini", asc = FALSE))[1])
print(xtable(as.table(sort(table(times), decreasing = TRUE)), caption = "Most important features for classificationPairs."), booktabs = TRUE)

modelrp = regressionPairs(makeLearner("regr.randomForest"), ldf)
resrp = data.frame(model = "regressionPairs",
    mean.misclassification.penalty = mean(misclassificationPenalties(ldf, modelrp)),
    solved = sum(successes(ldf, modelrp)),
    mean.performance = mean(parscores(ldf, modelrp, factor = 1)),
    median.performance = median(parscores(ldf, modelrp, factor = 1)))
times = sapply(modelrp$models, function(x) row.names(sortByCol(as.data.frame(x$learner.model$importance), "IncNodePurity", asc = FALSE))[1])
print(xtable(as.table(sort(table(times), decreasing = TRUE)), caption = "Most important features for regressionPairs."), booktabs = TRUE)

@@

pmod = data.frame(instance_id = unique(mod$predictions$instance_id), portfolio = parscores(ldf, mod, factor = 1))

perfs = subset(ldf$data, TRUE, c("instance_id", ldf$performance))
perfs = merge(perfs, vbs.agg, by = "instance_id")
perfs = merge(perfs, pmod, by = "instance_id")
wide = gather_(perfs, "solver", "time", names(perfs)[-1])
wide$type = ifelse(wide$solver %in% c("virtual.best", "portfolio"), "pf", "alg")
ggplot(wide, aes(x = time, col = solver, linetype = type)) + stat_ecdf() +
    scale_linetype_manual(values=c(3,1), guide = FALSE) +
    scale_x_log10(limits = c(10e-5, asscenario$desc$algorithm_cutoff_time)) +
    ylab("fraction of instances solved") +
    geom_vline(xintercept = asscenario$desc$algorithm_cutoff_time, col = "red")
@

@@

<<echo=FALSE, results='asis', warning=FALSE, message=FALSE>>=
resvbs = data.frame(model = "virtual best",
    mean.misclassification.penalty = mean(misclassificationPenalties(ldf3, vbs)),
    solved = sum(successes(ldf3, vbs)),
    mean.performance = mean(parscores(ldf3, vbs, factor = 1)),
    median.performance = median(parscores(ldf3, vbs, factor = 1)))
ressb = data.frame(model = "single best",
    mean.misclassification.penalty = mean(misclassificationPenalties(ldf3, singleBest)),
    solved = sum(successes(ldf3, singleBest)),
    mean.performance = mean(parscores(ldf3, singleBest, factor = 1)),
    median.performance = median(parscores(ldf3, singleBest, factor = 1)))

modelc = classify(rflearner, ldf3)
resc = data.frame(model = "classification",
    mean.misclassification.penalty = mean(misclassificationPenalties(ldf3, modelc)),
    solved = sum(successes(ldf3, modelc)),
    mean.performance = mean(parscores(ldf3, modelc, factor = 1)),
    median.performance = median(parscores(ldf3, modelc, factor = 1)))
times = sapply(modelc$models, function(x) row.names(sortByCol(as.data.frame(x$learner.model$importance), "MeanDecreaseGini", asc = FALSE))[1])
print(xtable(as.table(sort(table(times), decreasing = TRUE)), caption = "Most important features for classification."), booktabs = TRUE)

modelr = regression(makeLearner("regr.randomForest"), ldf3)
resr = data.frame(model = "regression",
    mean.misclassification.penalty = mean(misclassificationPenalties(ldf3, modelr)),
    solved = sum(successes(ldf3, modelr)),
    mean.performance = mean(parscores(ldf3, modelr, factor = 1)),
    median.performance = median(parscores(ldf3, modelr, factor = 1)))
times = sapply(modelr$models, function(x) row.names(sortByCol(as.data.frame(x$learner.model$importance), "IncNodePurity", asc = FALSE))[1])
print(xtable(as.table(sort(table(times), decreasing = TRUE)), caption = "Most important features for regression."), booktabs = TRUE)

modelcp = classifyPairs(rflearner, ldf3)
rescp = data.frame(model = "classifyPairs",
    mean.misclassification.penalty = mean(misclassificationPenalties(ldf3, modelcp)),
    solved = sum(successes(ldf3, modelcp)),
    mean.performance = mean(parscores(ldf3, modelcp, factor = 1)),
    median.performance = median(parscores(ldf3, modelcp, factor = 1)))
times = sapply(modelcp$models, function(x) row.names(sortByCol(as.data.frame(x$learner.model$importance), "MeanDecreaseGini", asc = FALSE))[1])
print(xtable(as.table(sort(table(times), decreasing = TRUE)), caption = "Most important features for classificationPairs."), booktabs = TRUE)

modelrp = regressionPairs(makeLearner("regr.randomForest"), ldf3)
resrp = data.frame(model = "regressionPairs",
    mean.misclassification.penalty = mean(misclassificationPenalties(ldf3, modelrp)),
    solved = sum(successes(ldf3, modelrp)),
    mean.performance = mean(parscores(ldf3, modelrp, factor = 1)),
    median.performance = median(parscores(ldf3, modelrp, factor = 1)))
times = sapply(modelrp$models, function(x) row.names(sortByCol(as.data.frame(x$learner.model$importance), "IncNodePurity", asc = FALSE))[1])
print(xtable(as.table(sort(table(times), decreasing = TRUE)), caption = "Most important features for regressionPairs."), booktabs = TRUE)

@@

<<echo=FALSE, results='asis', warning=FALSE, message=FALSE>>=
addmcp = rep.int(0, length(presolved))
addsucc = rep.int(1, length(presolved))
addtime = subset(ldf$data, ldf$data$instance_id %in% presolved)$lad_features

resvbs = data.frame(model = "virtual best",
    mean.misclassification.penalty = mean(misclassificationPenalties(ldf, vbs)),
    solved = sum(successes(ldf, vbs)),
    mean.performance = mean(parscores(ldf, vbs, factor = 1)),
    median.performance = median(parscores(ldf, vbs, factor = 1)))
ressb = data.frame(model = "single best",
    mean.misclassification.penalty = mean(misclassificationPenalties(ldf, singleBest)),
    solved = sum(successes(ldf, singleBest)),
    mean.performance = mean(parscores(ldf, singleBest, factor = 1)),
    median.performance = median(parscores(ldf, singleBest, factor = 1)))

resc = data.frame(model = "classification",
    mean.misclassification.penalty = mean(c(misclassificationPenalties(ldf3, modelc), addmcp)),
    solved = sum(c(successes(ldf3, modelc), addsucc)),
    mean.performance = mean(c(parscores(ldf3, modelc, factor = 1), addtime)),
    median.performance = median(c(parscores(ldf3, modelc, factor = 1), addtime)))

resr = data.frame(model = "regression",
    mean.misclassification.penalty = mean(c(misclassificationPenalties(ldf3, modelr), addmcp)),
    solved = sum(c(successes(ldf3, modelr), addsucc)),
    mean.performance = mean(c(parscores(ldf3, modelr, factor = 1), addtime)),
    median.performance = median(c(parscores(ldf3, modelr, factor = 1), addtime)))

rescp = data.frame(model = "classifyPairs",
    mean.misclassification.penalty = mean(c(misclassificationPenalties(ldf3, modelcp), addmcp)),
    solved = sum(c(successes(ldf3, modelcp), addsucc)),
    mean.performance = mean(c(parscores(ldf3, modelcp, factor = 1), addtime)),
    median.performance = median(c(parscores(ldf3, modelcp, factor = 1), addtime)))

resrp = data.frame(model = "regressionPairs",
    mean.misclassification.penalty = mean(c(misclassificationPenalties(ldf3, modelrp), addmcp)),
    solved = sum(c(successes(ldf3, modelrp), addsucc)),
    mean.performance = mean(c(parscores(ldf3, modelrp, factor = 1), addtime)),
    median.performance = median(c(parscores(ldf3, modelrp, factor = 1), addtime)))

tab = rbind(resvbs, ressb, resc, resr, rescp, resrp)
print(xtable(tab, digits = 3, caption = "Preliminary algorithm selection results with presolved instances removed (evaluated on all instances)."), booktabs = TRUE, include.rownames = FALSE)
@

@@

pmod = data.frame(instance_id = unique(mod$predictions$instance_id), portfolio = parscores(ldf3, mod, factor = 1))

perfs = subset(ldf3$data, TRUE, c("instance_id", ldf3$performance))
perfs = merge(perfs, vbs.agg, by = "instance_id")
perfs = merge(perfs, pmod, by = "instance_id")
wide = gather_(perfs, "solver", "time", names(perfs)[-1])
wide$type = ifelse(wide$solver %in% c("virtual.best", "portfolio"), "pf", "alg")
ggplot(wide, aes(x = time, col = solver, linetype = type)) + stat_ecdf() +
    scale_linetype_manual(values=c(3,1), guide = FALSE) +
    scale_x_log10(limits = c(10e-5, asscenario$desc$algorithm_cutoff_time)) +
    ylab("fraction of instances solved") +
    geom_vline(xintercept = asscenario$desc$algorithm_cutoff_time, col = "red")
@

<<echo=FALSE,fig.cap='ECDF for algorithms and portfolio for all instances (best model).'>>=
vbs.agg = aggregate(as.formula(paste("score~", paste(c("instance_id", "iteration"), sep="+", collapse="+"))), vbs(ldf), function(ss) { ss[1] })
vbs.agg$virtual.best = parscores(ldf, vbs, factor = 1)
vbs.agg$iteration = NULL
vbs.agg$score = NULL

pmod = data.frame(instance_id = unique(mod$predictions$instance_id), portfolio = parscores(ldf3, mod, factor = 1))
pmod = rbind(pmod, data.frame(instance_id = factor(presolved), portfolio = subset(ldf$data, ldf$data$instance_id %in% presolved)$lad_features))

perfs = subset(ldf$data, TRUE, c("instance_id", ldf$performance))
perfs = merge(perfs, vbs.agg, by = "instance_id")
perfs = merge(perfs, pmod, by = "instance_id")
wide = gather_(perfs, "solver", "time", names(perfs)[-1])
wide$type = ifelse(wide$solver %in% c("virtual.best", "portfolio"), "pf", "alg")
ggplot(wide, aes(x = time, col = solver, linetype = type)) + stat_ecdf() +
    scale_linetype_manual(values=c(3,1), guide = FALSE) +
    scale_x_log10(limits = c(10e-5, asscenario$desc$algorithm_cutoff_time)) +
    ylab("fraction of instances solved") +
    geom_vline(xintercept = asscenario$desc$algorithm_cutoff_time, col = "red")
@

@@

<<echo=FALSE, results='asis', warning=FALSE, message=FALSE>>=
resvbs = data.frame(model = "virtual best",
    mean.misclassification.penalty = mean(misclassificationPenalties(ldf2, vbs)),
    solved = sum(successes(ldf2, vbs)),
    mean.performance = mean(parscores(ldf2, vbs, factor = 1)),
    median.performance = median(parscores(ldf2, vbs, factor = 1)))
ressb = data.frame(model = "single best",
    mean.misclassification.penalty = mean(misclassificationPenalties(ldf2, singleBest)),
    solved = sum(successes(ldf2, singleBest)),
    mean.performance = mean(parscores(ldf2, singleBest, factor = 1)),
    median.performance = median(parscores(ldf2, singleBest, factor = 1)))

modelc = classify(rflearner, ldf2)
resc = data.frame(model = "classification",
    mean.misclassification.penalty = mean(misclassificationPenalties(ldf2, modelc)),
    solved = sum(successes(ldf2, modelc)),
    mean.performance = mean(parscores(ldf2, modelc, factor = 1)),
    median.performance = median(parscores(ldf2, modelc, factor = 1)))
times = sapply(modelc$models, function(x) row.names(sortByCol(as.data.frame(x$learner.model$importance), "MeanDecreaseGini", asc = FALSE))[1])
print(xtable(as.table(sort(table(times), decreasing = TRUE)), caption = "Most important features for classification."), booktabs = TRUE)

modelr = regression(makeLearner("regr.randomForest"), ldf2)
resr = data.frame(model = "regression",
    mean.misclassification.penalty = mean(misclassificationPenalties(ldf2, modelr)),
    solved = sum(successes(ldf2, modelr)),
    mean.performance = mean(parscores(ldf2, modelr, factor = 1)),
    median.performance = median(parscores(ldf2, modelr, factor = 1)))
times = sapply(modelr$models, function(x) row.names(sortByCol(as.data.frame(x$learner.model$importance), "IncNodePurity", asc = FALSE))[1])
print(xtable(as.table(sort(table(times), decreasing = TRUE)), caption = "Most important features for regression."), booktabs = TRUE)

modelcp = classifyPairs(rflearner, ldf2)
rescp = data.frame(model = "classifyPairs",
    mean.misclassification.penalty = mean(misclassificationPenalties(ldf2, modelcp)),
    solved = sum(successes(ldf2, modelcp)),
    mean.performance = mean(parscores(ldf2, modelcp, factor = 1)),
    median.performance = median(parscores(ldf2, modelcp, factor = 1)))
times = sapply(modelcp$models, function(x) row.names(sortByCol(as.data.frame(x$learner.model$importance), "MeanDecreaseGini", asc = FALSE))[1])
print(xtable(as.table(sort(table(times), decreasing = TRUE)), caption = "Most important features for classificationPairs."), booktabs = TRUE)

modelrp = regressionPairs(makeLearner("regr.randomForest"), ldf2)
resrp = data.frame(model = "regressionPairs",
    mean.misclassification.penalty = mean(misclassificationPenalties(ldf2, modelrp)),
    solved = sum(successes(ldf2, modelrp)),
    mean.performance = mean(parscores(ldf2, modelrp, factor = 1)),
    median.performance = median(parscores(ldf2, modelrp, factor = 1)))
times = sapply(modelrp$models, function(x) row.names(sortByCol(as.data.frame(x$learner.model$importance), "IncNodePurity", asc = FALSE))[1])
print(xtable(as.table(sort(table(times), decreasing = TRUE)), caption = "Most important features for regressionPairs."), booktabs = TRUE)

@@

<<echo=FALSE, results='asis', warning=FALSE, message=FALSE>>=
vf2pre = setdiff(ldf3$data$instance_id, ldf2$data$instance_id)
addmcp = rep.int(0, length(presolved) + length(vf2pre))
addsucc = rep.int(1, length(presolved) + length(vf2pre))
addtime = c(subset(ldf$data, ldf$data$instance_id %in% presolved)$lad_features, subset(ldf$data, ldf$data$instance_id %in% vf2pre)$vf2)

resvbs = data.frame(model = "virtual best",
    mean.misclassification.penalty = mean(misclassificationPenalties(ldf, vbs)),
    solved = sum(successes(ldf, vbs)),
    mean.performance = mean(parscores(ldf, vbs, factor = 1)),
    median.performance = median(parscores(ldf, vbs, factor = 1)))
ressb = data.frame(model = "single best",
    mean.misclassification.penalty = mean(misclassificationPenalties(ldf, singleBest)),
    solved = sum(successes(ldf, singleBest)),
    mean.performance = mean(parscores(ldf, singleBest, factor = 1)),
    median.performance = median(parscores(ldf, singleBest, factor = 1)))

resc = data.frame(model = "classification",
    mean.misclassification.penalty = mean(c(misclassificationPenalties(ldf2, modelc), addmcp)),
    solved = sum(c(successes(ldf2, modelc), addsucc)),
    mean.performance = mean(c(parscores(ldf2, modelc, factor = 1), addtime)),
    median.performance = median(c(parscores(ldf2, modelc, factor = 1), addtime)))

resr = data.frame(model = "regression",
    mean.misclassification.penalty = mean(c(misclassificationPenalties(ldf2, modelr), addmcp)),
    solved = sum(c(successes(ldf2, modelr), addsucc)),
    mean.performance = mean(c(parscores(ldf2, modelr, factor = 1), addtime)),
    median.performance = median(c(parscores(ldf2, modelr, factor = 1), addtime)))

rescp = data.frame(model = "classifyPairs",
    mean.misclassification.penalty = mean(c(misclassificationPenalties(ldf2, modelcp), addmcp)),
    solved = sum(c(successes(ldf2, modelcp), addsucc)),
    mean.performance = mean(c(parscores(ldf2, modelcp, factor = 1), addtime)),
    median.performance = median(c(parscores(ldf2, modelcp, factor = 1), addtime)))

resrp = data.frame(model = "regressionPairs",
    mean.misclassification.penalty = mean(c(misclassificationPenalties(ldf2, modelrp), addmcp)),
    solved = sum(c(successes(ldf2, modelrp), addsucc)),
    mean.performance = mean(c(parscores(ldf2, modelrp, factor = 1), addtime)),
    median.performance = median(c(parscores(ldf2, modelrp, factor = 1), addtime)))

tab = rbind(resvbs, ressb, resc, resr, rescp, resrp)
print(xtable(tab, digits = 3, caption = "Preliminary algorithm selection results with presolver (evaluated on all instances)."), booktabs = TRUE, include.rownames = FALSE)
@

@@

pmod = data.frame(instance_id = unique(mod$predictions$instance_id), portfolio = parscores(ldf2, mod, factor = 1))

perfs = subset(ldf2$data, TRUE, c("instance_id", ldf2$performance))
perfs = merge(perfs, vbs.agg, by = "instance_id")
perfs = merge(perfs, pmod, by = "instance_id")
wide = gather_(perfs, "solver", "time", names(perfs)[-1])
wide$type = ifelse(wide$solver %in% c("virtual.best", "portfolio"), "pf", "alg")
ggplot(wide, aes(x = time, col = solver, linetype = type)) + stat_ecdf() +
    scale_linetype_manual(values=c(3,1), guide = FALSE) +
    scale_x_log10(limits = c(10e-5, asscenario$desc$algorithm_cutoff_time)) +
    ylab("fraction of instances solved") +
    geom_vline(xintercept = asscenario$desc$algorithm_cutoff_time, col = "red")
@

<<echo=FALSE,fig.cap='ECDF for algorithms and portfolio for all instances (best model).'>>=
vbs.agg = aggregate(as.formula(paste("score~", paste(c("instance_id", "iteration"), sep="+", collapse="+"))), vbs(ldf), function(ss) { ss[1] })
vbs.agg$virtual.best = parscores(ldf, vbs, factor = 1)
vbs.agg$iteration = NULL
vbs.agg$score = NULL

pmod = data.frame(instance_id = unique(mod$predictions$instance_id), portfolio = parscores(ldf2, mod, factor = 1))
pmod = rbind(pmod, data.frame(instance_id = factor(presolved), portfolio = subset(ldf$data, ldf$data$instance_id %in% presolved)$lad_features))
vf2pre = setdiff(ldf3$data$instance_id, ldf2$data$instance_id)
pmod = rbind(pmod, data.frame(instance_id = factor(vf2pre), portfolio = subset(ldf$data, ldf$data$instance_id %in% vf2pre)$vf2))

perfs = subset(ldf$data, TRUE, c("instance_id", ldf$performance))
perfs = merge(perfs, vbs.agg, by = "instance_id")
perfs = merge(perfs, pmod, by = "instance_id")
wide = gather_(perfs, "solver", "time", names(perfs)[-1])
wide$type = ifelse(wide$solver %in% c("virtual.best", "portfolio"), "pf", "alg")
ggplot(wide, aes(x = time, col = solver, linetype = type)) + stat_ecdf() +
    scale_linetype_manual(values=c(3,1), guide = FALSE) +
    scale_x_log10(limits = c(10e-5, asscenario$desc$algorithm_cutoff_time)) +
    ylab("fraction of instances solved") +
    geom_vline(xintercept = asscenario$desc$algorithm_cutoff_time, col = "red")
@
